### 2023-09-02 paper/FPF-WG1.tex
Minor corrections

Proton-proton collisions at the LHC generate a high-intensity collimated beam of neutrinos
in the forward (beam) direction, characterised by energies of up to several TeV.
%
The recent  observation of LHC neutrinos by FASER$\nu$ and SND@LHC
signals that this hitherto ignored particle beam is now available for scientific inquiry.
%
Here we quantify the impact that neutrino deep-inelastic scattering (DIS) structure function
measurements at the LHC would have
on the parton distributions (PDFs) of protons and heavy nuclei.
%
We generate projections for DIS structure functions
at FASER$\nu$ and SND@LHC,
as well as at the FASER$\nu$2, AdvSND, and FLArE experiments
to be  hosted at the proposed
Forward Physics Facility (FPF) operating concurrently with the High-Luminosity LHC.
%
These measurements are found to cover a kinematic region in $x$ and $Q^2$ comparable to that
of the upcoming Electron-Ion Collider, with sub-percent statistical uncertainties
in the FPF case.
%
Including these DIS projections into global (n)PDF analyses, specifically PDF4LHC21, NNPDF4.0,
 and EPPS21,  reveals a significant reduction of PDF uncertainties, in particular
 for strangeness and the up and down valence PDFs.
 %
 We demonstrate that LHC neutrino data enables improved theoretical
 predictions for core processes at the HL-LHC, such as Higgs and weak gauge (di)boson production.
%
 Our analysis highlights how exploiting the LHC neutrino beam effectively
provides CERN with a new ``Neutrino-Ion Collider''.

>>>>

Proton-proton collisions at the LHC generate a high-intensity collimated beam of neutrinos
in the forward (beam) direction, characterised by energies of up to several TeV.
%
The recent  observation of LHC neutrinos by FASER$\nu$ and SND@LHC
signals that this hitherto ignored particle beam is now available for scientific inquiry.
%
Here we quantify the impact that neutrino deep-inelastic scattering (DIS) structure function
measurements at the LHC would have
on the parton distributions (PDFs) of protons and heavy nuclei.
%
We generate projections for DIS structure functions
at FASER$\nu$ and SND@LHC,
as well as at the FASER$\nu$2, AdvSND, and FLArE experiments
to be  hosted at the proposed
Forward Physics Facility (FPF) operating concurrently with the High-Luminosity LHC (HL-LHC).
%
These measurements are found to cover a kinematic region in $x$ and $Q^2$ comparable to that
of the upcoming Electron-Ion Collider, with sub-percent statistical uncertainties
in the FPF case.
%
Including these DIS projections into global (n)PDF analyses, specifically PDF4LHC21, NNPDF4.0,
 and EPPS21,  reveals a significant reduction of PDF uncertainties, in particular
 for strangeness and the up and down valence PDFs.
 %
 We demonstrate that LHC neutrino data enables improved theoretical
 predictions for core processes at the HL-LHC, such as Higgs and weak gauge (di)boson production.
%
 Our analysis highlights how exploiting the LHC neutrino beam effectively
provides CERN with a new ``Neutrino-Ion Collider''.

### 2023-09-02 paper/sec-pheno.tex
some polishing
Minor corrections

\clearpage
\section{Implications for HL-LHC processes}
\label{sec:pheno}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-global.pdf}
\caption{Same as Fig.~\ref{fig:NNPDF40_pheno_integrated}
for the corresponding differential distributions.
%
}
\label{fig:NNPDF40_pheno_differential}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

\section{Implications for HL-LHC processes}
\label{sec:pheno}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-global.pdf}
\caption{Same as Fig.~\ref{fig:NNPDF40_pheno_integrated}
for the corresponding differential distributions.
%
}
\label{fig:NNPDF40_pheno_differential}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
	\centering
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\caption{
		Same as Fig.~\ref{fig:NNPDF40_pheno_integrated} but with PDF4LHC21.
		}
	\label{fig:PDF4LHC21_pheno_integrated}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-global-pdf4lhc21.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-global-pdf4lhc21.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-global-pdf4lhc21.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-global-pdf4lhc21.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-global-pdf4lhc21.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-global-pdf4lhc21.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-global-pdf4lhc21.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-global-pdf4lhc21.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-global-pdf4lhc21.pdf}
	\caption{
		Same as Fig.~\ref{fig:NNPDF40_pheno_differential} but with PDF4LHC21.
	}
	\label{fig:PDF4LHC21_pheno_differential}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
